Response to Pachter’s Review

### 2020-01-28 index.Rmd
revision

---
title: "Response to Pachter’s Review"
author: "Joshua Paik and Igor Rivin"
date: '1/22/2020, Last Update: 1/23/2020 3:16 A.M. G.M.T.'
output:
  pdf_document:
    keep_tex: yes
    toc: yes
  html_document:
    toc: yes
---

@@

We would like to thank Lior for finding the bug in our appendix which pushes the mean Google Scholar citations of B further away from A. We agree that the sentence - “while this is not optimal, a quick sample size calculation shows that one needs 303 samples or 21% of the data to produce statistics at a 95% confidence level and a 5% confidence interval.” - is ridiculous.

@@

We will compare the mean number of citations and citations per year between signers of Letters A, B, and C. We will validate the significance of the difference between signers using a [permutation test](https://en.wikipedia.org/wiki/Resampling_(statistics)#Permutation_tests).

@@

```{r, echo = FALSE}
plot(df$age,df$amscitperyear, main = "Age vs. MSN Citations per Year Revised Dataset")
abline(linearmodel1, col = "red")
```

@@

### Citations per Year vs Age
We plot the Age vs Citations per Year for all math R1. We generate a linear regression model and output a 95% confidence interval for the slope. 
```{r, echo=FALSE}
linearmodel2 <- lm(allR1$citperyear ~ allR1$age, data = allR1)
plot(allR1$age, allR1$citperyear, main="Age vs Citations per Year All Math R1")
abline(linearmodel2,col="red") 
```

@@

So while visually it appears that there is no correlation between citations and citations per year, one may object and say, the slope is positive! Which leads to the following question.

@@

This method was suggested by a friend as a final check to eliminate any question that age was the greatest confounder. We want to show that $\mu(A) < \mu(B \cup C)$. We will randomly sample a population of 20 from A, called $X$. For each member $x \in X$, we will find every person from B and C that is within a two year age interval from $x$. We will randomly sample one, and induce a new population $Y$. Then we will compare the means by storing X-Y. We repeat this 1,000 times and plot a histogram of the induced values. If 0 is within this new distribution, then maybe there is a chance, a totally slim one after above, that in fact age is a confounder. If the distribution is primarily negative, then X < Y. Otherwise X > Y. We perform this analysis with both AMS citations and Google Scholar citations.

@@

Temple has an average citations per year of 12.33, so we retract our claim that letter A is comparable to Temple. It is closer to the University of Massachusetts - Amherst  which has an average citations per year of 16.17. By [US News](https://www.usnews.com/best-graduate-schools/top-science-schools/mathematics-rankings), University of Massachusetts - Amherst's Math Department has a rank of 55. Rutgers has an average citations per year of 35.01, so we retract our claim that letter B is comparable to Rutgers. It is closer to the University of Minesotta which has an average citations per year of 42.07 and a US News Ranking of 19. For Letter C, we claimed that it was another tier higher - indeed it is closer to the University of Chicago, which has an average citations per year of 56.27, ranked 6 by US News.

An astute observer would notice we are not exactly comparing apples to apples. Presumably ones first publication could be before one finishes their PhD. So even with the boost, the order amongst letter signers stands.

@@

We have debunked the claim that age is the greatest contributor for the difference in citations and citations per year between signers of Letter A, B, and C. Indeed, the least meritorious of mathematicians as a whole signed letter A, whereas the more meritorious signed letters B and C, with merit judged by citations. If one was not willing to believe citations impose even a small order on merit, one could replace citations with Fields medals, AMS Fellowships, or many other metrics.

>>>>

---
title: "Response to Pachter’s Review"
author: "Joshua Paik and Igor Rivin"
date: '1/22/2020, Last Update: 1/28/2020 6:00 P.M. G.M.T.'
output:
  html_document:
    toc: yes
  pdf_document:
    keep_tex: yes
    toc: yes
---

@@

We would like to thank Pachter for finding the bug in our appendix which pushes the mean Google Scholar citations of B further away from A. We agree that the sentence - “while this is not optimal, a quick sample size calculation shows that one needs 303 samples or 21% of the data to produce statistics at a 95% confidence level and a 5% confidence interval.” - is ridiculous.

@@

We will compare the mean number of citations and citations per year (that is years elapsed since completion of PhD) between signers of Letters A, B, and C. We will validate the significance of the difference between signers using a [permutation test](https://en.wikipedia.org/wiki/Resampling_(statistics)#Permutation_tests).

@@

```{r, echo = FALSE}
plot(df$age,df$amscitperyear, main = "MSN Citations per Year vs Age Revised Dataset")
abline(linearmodel1, col = "red")
```

@@

### Citations per Year vs Age
We plot the Citations per Year vs Age for all math R1. We generate a linear regression model and output a 95% confidence interval for the slope. 
```{r, echo=FALSE}
linearmodel2 <- lm(allR1$citperyear ~ allR1$age, data = allR1)
plot(allR1$age, allR1$citperyear, main="Citations per Year vs Age All Math R1")
abline(linearmodel2,col="red") 
```

@@

So while visually it appears that there is no correlation between year and citations per year, one may object and say, the slope is positive! Which leads to the following question.

@@

This method was suggested by a friend as a final check to eliminate any question that age was the greatest confounder. We want to show that $\mu(A) < \mu(B \cup C)$. We will randomly sample a population of 20 from A, called $X$. For each member $x \in X$, we will find every person from B and C that is within a four year age interval from $x$. We will randomly sample one, and induce a new population $Y$. Then we will compare the means by storing X-Y. We repeat this 1,000 times and plot a histogram of the induced values. If 0 is within this new distribution, then maybe there is a chance, a totally slim one after above, that in fact age is a confounder. If the distribution is primarily negative, then X < Y. Otherwise X > Y. We perform this analysis with both AMS citations and Google Scholar citations.

@@

Temple has an average citations per year of 12.33, so we retract our claim that letter A is comparable to Temple. It is closer to the University of Massachusetts - Amherst  which has an average citations per year of 16.17. By [US News](https://www.usnews.com/best-graduate-schools/top-science-schools/mathematics-rankings), University of Massachusetts - Amherst's Math Department has a rank of 55. Rutgers has an average citations per year of 35.01, so we retract our claim that letter B is comparable to Rutgers. It is closer to the University of Minesota which has an average citations per year of 42.07 and a US News Ranking of 19. For Letter C, we claimed that it was another tier higher - indeed it is closer to the University of Chicago, which has an average citations per year of 56.27, ranked 6 by US News.

An astute observer would notice we are not exactly comparing apples to apples. Presumably one's first publication could be before one finishes their PhD. So even with the boost, the order amongst letter signers stands.

@@

We have debunked the claim that age is the confounder for the difference in citations and citations per year between signers of Letter A, B, and C. Indeed, the least meritorious of mathematicians as a whole signed letter A, whereas the more meritorious signed letters B and C, with merit judged by citations. If one was not willing to believe citations impose even a small order on merit, one could replace citations with Fields medals, AMS Fellowships, or many other metrics.
